### 2017-08-24 paper/incomeShocks-jde-r1.tex
Add education results to appendix

\begin{table}[htbp]
\begin{center}
\begin{small}
\begin{threeparttable}
\caption{The Effects of Crop Loss on Contraceptives Use by Education Level}
\label{tab:education}
\begin{tabular}{@{} l D{.}{.}{1.5} D{.}{.}{1.5}  D{.}{.}{1.5} D{.}{.}{1.5} D{.}{.}{1.5}  @{}}
\toprule
                                                       & \mco{}              &\mco{}               &\multicolumn{3}{c}{Contraceptive Use}\\ \cmidrule(lr){4-6}
                                                       & \mco{Pregnant}      &\mco{Birth}          &\mco{Any}            &\mco{Traditional}    & \mco{Modern}        \\ \midrule
                                                       & \multicolumn{5}{c}{Respondent's education level} \\
Crop loss \X no education                              &      -0.069         &                     &       0.080         &       0.041         &       0.032         \\
                                                       &     (0.062)         &                     &     (0.051)         &     (0.041)         &     (0.029)         \\
Crop loss \X 1-6 years of education                    &      -0.006         &                     &       0.019         &       0.036         &      -0.033         \\
                                                       &     (0.063)         &                     &     (0.051)         &     (0.040)         &     (0.031)         \\
Crop loss \X 7 plus years of education                 &      -0.167\sym{***}&                     &       0.098\sym{**} &       0.073\sym{*}  &       0.009         \\
                                                       &     (0.050)         &                     &     (0.043)         &     (0.039)         &     (0.018)         \\
Crop loss (7-14 months)                                &                     &      -0.165\sym{**} &                     &                     &                     \\
\hs \X no education                                    &                     &     (0.064)         &                     &                     &                     \\
Crop loss (7-14 months)                                &                     &      -0.115         &                     &                     &                     \\
\hs \X 1-6 years of education                          &                     &     (0.072)         &                     &                     &                     \\
Crop loss (7-14 months)                                &                     &      -0.185\sym{***}&                     &                     &                     \\
\hs \X 7 plus years of education                       &                     &     (0.062)         &                     &                     &                     \\
% \addlinespace 
% Observations                                           &    \mco{988}        &    \mco{741}        &    \mco{988}        &    \mco{988}        &    \mco{988}        \\
% Number of women                                        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        \\
\addlinespace 
                                                       & \multicolumn{5}{c}{Head's education level} \\
Crop loss \X no education                              &      -0.071         &                     &       0.168\sym{**} &       0.149\sym{**} &       0.017         \\
                                                       &     (0.074)         &                     &     (0.080)         &     (0.069)         &     (0.040)         \\
Crop loss \X 1-6 years of education                    &      -0.024         &                     &       0.017         &       0.006         &      -0.015         \\
                                                       &     (0.061)         &                     &     (0.049)         &     (0.039)         &     (0.030)         \\
Crop loss \X 7 plus years of education                 &      -0.147\sym{***}&                     &       0.083\sym{**} &       0.062\sym{*}  &       0.013         \\
                                                       &     (0.048)         &                     &     (0.040)         &     (0.036)         &     (0.017)         \\
Crop loss (7-14 months)                                &                     &      -0.083         &                     &                     &                     \\
\hs \X no education                                    &                     &     (0.095)         &                     &                     &                     \\
Crop loss (7-14 months)                                &                     &      -0.137\sym{**} &                     &                     &                     \\
\hs \X 1-6 years of education                          &                     &     (0.066)         &                     &                     &                     \\
Crop loss (7-14 months)                                &                     &      -0.194\sym{***}&                     &                     &                     \\
\hs \X 7 plus years of education                       &                     &     (0.057)         &                     &                     &                     \\
% \addlinespace 
% Observations                                           &    \mco{964}        &    \mco{723}        &    \mco{964}        &    \mco{964}        &    \mco{964}        \\
% Number of women                                        &    \mco{241}        &    \mco{241}        &    \mco{241}        &    \mco{241}        &    \mco{241}        \\
% \addlinespace 
%                                                        & \multicolumn{5}{c}{Maximum education level in household} \\
% Crop loss \X no education                              &      -0.396\sym{***}&                     &       0.503         &       0.494         &       0.005         \\
%                                                        &     (0.026)         &                     &     (0.371)         &     (0.372)         &     (0.012)         \\
% Crop loss \X 1-6 years of education                    &      -0.016         &                     &       0.067         &       0.032         &       0.011         \\
%                                                        &     (0.065)         &                     &     (0.069)         &     (0.053)         &     (0.045)         \\
% Crop loss \X 7 plus years of education                 &      -0.114\sym{**} &                     &       0.064\sym{**} &       0.054\sym{**} &       0.000         \\
%                                                        &     (0.046)         &                     &     (0.032)         &     (0.026)         &     (0.014)         \\
% Crop loss (7-14 months)                                &                     &      -0.322\sym{*}  &                     &                     &                     \\
% \hs \X no education                                    &                     &     (0.176)         &                     &                     &                     \\
% Crop loss (7-14 months)                                &                     &      -0.118\sym{*}  &                     &                     &                     \\
% \hs \X 1-6 years of education                          &                     &     (0.071)         &                     &                     &                     \\
% Crop loss (7-14 months)                                &                     &      -0.170\sym{***}&                     &                     &                     \\
% \hs \X 7 plus years of education                       &                     &     (0.054)         &                     &                     &                     \\
\addlinespace 
Wave dummies                                           &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Woman fixed effects                                    &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Observations                                           &    \mco{988}        &    \mco{741}        &    \mco{988}        &    \mco{988}        &    \mco{988}        \\
Number of women                                        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        \\
\bottomrule
\end{tabular}
\begin{tablenotes} \footnotesize
\item \hspace*{-0.5em} \textbf{Note.}
Robust standard errors clustered at household level in parentheses; 
* significant at 10\%; ** significant at 5\%; *** significant at 1\%.
Crop loss is a dummy for a per capita crop loss of 200 TZS or above.
Assets are per capita and measured in 10,000 TZS.
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{center}
\end{table}

>>>>

% Effects of Crop Loss on Contraceptives Use by Education Level
\input{../tables/appendix_education.tex}
